Overview

### 2019-03-15 notebooks/general_info.Rmd
got numbers all the way up to folding ints and doubles together. barely any poly left. time to pull up colocation of character/real poly and lists

What if we roll NULL into every type?

>>>>

What if we roll NULL into every type?
```{r}
los_basic_no_null <- lapply(los_basic, function(lof) {lapply(lof, function(df) {fold_NULL_into_other_types_df(df)})})
```

What are the counts now?
```{r}
total_mono_type_basic_no_null <- apply_count_to_lopkg_c(los_basic_no_null, args_count_all_mono_type)
total_mono_all_basic_no_null <- apply_count_to_lopkg_c(los_basic_no_null, args_count_all_mono_all)
```

Great.
Now, what are the top instances of type-based polymorphism?
```{r}
poly_type_args_basic_no_null <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los_basic_no_null, extract_poly_type_args))
poly_type_args_basic_no_null <- poly_type_args_basic_no_null[order(-poly_type_args_basic_no_null$count),] # sort by count
poly_type_args_basic_no_null$perc <- round(poly_type_args_basic_no_null$count/sum(poly_type_args_basic_no_null$count) * 100, 2)
```

What's the top?
```{r}
format_df_for_print(poly_type_args_basic_no_null[1:20,])
```

So, clearly, "real number polymorphism" is the top choice.
What if we fold ints and doubles together into reals?

```{r}
los_basic_no_null_real <- lapply(los_basic_no_null, function(lof) {lapply(lof, function(df) {fold_together_int_double_df(df)})})
```
